Cards persistent analysis

### 2019-12-06 cards_persistent_analysis.Rmd
A note
Some tweaks and a non-productive selection technique

```{r}
parent_dir = "."
subdirs = c("results_for_humans_with_library_2", "results_for_humans_with_library_3",
            #"results_for_humans_with_library_persistent",  "results_for_humans_with_library_persistent_2", "results_for_humans_with_library_persistent_3",  "results_for_humans_with_library_persistent_4", 
            "results_for_humans_with_library_persistent_5",  "results_for_humans_with_library_persistent_6",
            "results_for_humans_with_library_persistent_7", 
            "results_for_humans_with_library_persistent_8", 
            "results_for_humans_with_library_persistent_9"
            )
num_runs = 3
```

@@

```{r}
selected_meta_true_d = meta_true_d %>%
  filter(meta_task=="toggle_losers",
         base_task_toe == "example_is_train" | source == "game_straight_flush_l_0_bv_0_sr_0") %>%
  group_by(run_type, run, epoch, base_task_toe) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(base_task_toe, mean_loss) %>%
  group_by(run_type, run) %>%
  filter(example_is_train == max(example_is_train))
selected_meta_true_d %>%
  arrange(desc(example_is_train))

@@

>>>>

```{r}
parent_dir = "."
subdirs = c(#"results_for_humans_with_library_2", 
            "results_for_humans_with_library_3", "results_for_humans_with_library_4",
            #"results_for_humans_with_library_persistent",  "results_for_humans_with_library_persistent_2", "results_for_humans_with_library_persistent_3",  "results_for_humans_with_library_persistent_4", 
            "results_for_humans_with_library_persistent_5",  "results_for_humans_with_library_persistent_6",
            #"results_for_humans_with_library_persistent_7", 
            #"results_for_humans_with_library_persistent_8", 
            "results_for_humans_with_library_persistent_9",
            "results_for_humans_with_library_persistent_10"
            )
num_runs = 2
```

@@

This seems to be a good criteria for persistent reps, but interestingly not for non-persistent.
```{r}
selected_meta_true_d = meta_true_d %>%
  filter(meta_task=="toggle_losers",
         base_task_toe == "example_is_train" | source == "game_straight_flush_l_0_bv_0_sr_0") %>%
  group_by(run_type, run, epoch, base_task_toe) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(base_task_toe, mean_loss) %>%
  group_by(run_type, run) %>%
  filter(example_is_train == max(example_is_train))
selected_meta_true_d %>%
  arrange(desc(example_is_train))

@@

This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other.

```{r}
selected_meta_true_d_3 = meta_true_d %>%
  filter(meta_task=="toggle_losers",
         !grepl("persistent", run_type)) %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  mutate(train_and_other = train + eval_other) %>%
  group_by(run_type, run) %>%
  filter(train_and_other == max(train_and_other))
selected_meta_true_d_3 %>%
  arrange(desc(train_and_other))
```
